Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-04-21 paper.qmd
scaling data...right

When $k=2$ which is assumed for hexagon binning, $(y_{1,\text{max}}=1$ and $y_{2,\text{max}} = \frac{r_2}{r_1}\times \frac{2}{\sqrt{3}}$. (The $\frac{2}{\sqrt{3}}$ accounts for the different height and width of a regular hexagon.)

>>>>

When $k=2$ which is assumed for hexagon binning, $y_{1,\text{max}}=1$ and $y_{2,\text{max}} = \frac{r_2}{r_1}\times \frac{2}{\sqrt{3}}$. (The $\frac{2}{\sqrt{3}}$ accounts for the different height ($h_b$) and width ($w_b$) of a regular hexagon.)
